---
title: "An Estimate On The Figures Of Live Animal And Animal Meat Imports Of World Countries"
author: 
  - Eryılmaz, Fatma Zühal[^1]
bibliography: ../bibliography/biblio.bib
csl: ../csl/apa.csl
header-includes:
  - \usepackage{polyglossia}
  - \setmainlanguage{english}
  - \usepackage{booktabs}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=8pt}
output:
  bookdown::pdf_document2:
    fig_caption: yes
    fig_height: 3
    fig_width: 4
    keep_tex: no
    latex_engine: xelatex
    number_sections: yes
    toc: no
geometry: margin=1in
link-citations: yes
urlcolor: blue
fontsize: 12pt
biblio-style: apalike
abstract: |
   Meat consumption is linked not only to macroeconomic uncertainties and GDP shocks, but also to living standards, nutrition, animal production and consumer prices. Meat is characterized by higher production costs and higher producer prices than other raw materials. Demand for meat is associated with rising incomes and changes in food consumption due to urbanization, with a preference for higher levels of protein from animal sources in the diet. While the global meat industry provides food and livelihoods for billions of people, it also has a significant impact on the environment and the health of the planet. 
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = FALSE, echo = TRUE, message = FALSE, warning = FALSE)
```

<!-- ======================================================================= -->
<!-- ============================== FOOTNOTES ============================== -->
<!-- ======================================================================= -->
[^1]: 20080389, [Github Repo](https://github.com/zuhaleryilmaz/final)




# Introduction
Live animal imports are important because different species need to be brought in to ensure continued breeding. However, live animal imports also come with many risks. When health screenings for live animals imported from different countries are not sufficiently conducted, the spread of animal diseases is inevitable. This situation can threaten a country's own animal population and cause problems throughout the food supply chain.

Animal meat imports are a more widespread practice than live animal imports. Many countries import animal meat to meet their own meat consumption needs. The most important reason for animal meat imports is that countries cannot meet their own meat consumption needs. Furthermore, imported animals must meet high standards in terms of both health and quality. Therefore, countries that will engage in animal meat imports have some restrictions.

While live animal and animal meat imports can provide many economic benefits, they can be risky for local producers. The import sector may reduce the business volume and increase the costs of local producers. However, it is believed that the quality and low prices of imports can contribute to the development of the animal meat sector in the country.

Countries can promote local production while conducting controlled imports by collaborating with governments and local sectors. In this way, both local producers can be supported and the benefits of imports can be maximized. The importance of live animal and animal meat imports worldwide, as well as the risks they pose, should be managed consciously and systematically.

According to the past years’ live animal and animal meat import figures, it is predicted that this trend will continue in 2023. Live animal and animal meat import is an important sector worldwide. It is believed that developing a strategy to increase their own production will help countries mitigate the environmental, health, and economic risks that this trade can pose.

## Literature Review

The literature emphasizes the need for transparency and collaboration among different countries and stakeholders in the trade of live animals and animal products. @narrod:2014 The exchange of information on animal health and disease outbreaks, as well as the adoption of common standards and best practices, can help reduce the risk of disease spread and facilitate trade. Meat trade flows among countries and world regions are determined largely by differences among countries in their resource base, their preferences for meat types and cuts, the extent and character of barriers to trade, and the industry structure (@galloway:2007).

In addition, some experts also call for a shift towards more sustainable and ethical practices in the global food supply chain, including reducing the dependence on animal-based products and promoting local production and consumption. @nelson:2003 This approach can not only help reduce the risks associated with the trade of live animals and animal products but also contribute to the broader goals of environmental sustainability, animal welfare, and public health in Turkey (@aydogdu:2018)

# Data


My Dataset Kaggle.com i bought it from his site.After transferring the yield to the program, na.i cleaned it with the omit code.I have determined the data I will use and created tables for them.

https://data.oecd.org/agroutput/meat-consumption.htm

OECD/FAO (2017), ”OECD-FAO Agricultural Outlook", OECD Agriculture statistics (database). doi: dx.doi.org/10.1787/agr-outl-data-en (Accessed on 24 January 2018)



A summary table shows which types of meat are consumed more and which types are consumed less. Additionally, we can observe how consumption varies by meat type and which types have a more even distribution.The results in this table can also be used to further analyze and strategize performance differences between multiple meats.


```{r, echo=FALSE}
library(tidyverse)
library(dplyr)
library(magrittr)
library(summariser)
```


```{r, echo=FALSE}
library(xtable) 
library(summarytools)
st_options(lang = "en")
```

```{r, echo=FALSE}
library(tidyverse)
m.eat <- read_csv("C:\\Users\\90546\\Desktop\\final\\data\\m.eat.csv")
```




# Methods and Data Analysis



```{r, echo=FALSE}
library(xtable) 
library(summarytools)
st_options(lang = "en")

```

```{r, echo=FALSE}
library(tidyverse)
m.eat <- read_csv("C:\\Users\\90546\\Desktop\\final\\data\\m.eat.csv")

```
```{r, echo=FALSE}
meatdf_kg <- m.eat %>% 
  filter(MEASURE == 'KG_CAP') %>% 
  select(-MEASURE) %>% 
  rename(VALUE_KG_CAP = Value)
View(meatdf_kg)

```
```{r, echo=FALSE}
meatdf_kg_type <- meatdf_kg %>% 
  group_by(LOCATION, SUBJECT) %>% 
  summarize(VALUE_KG_CAP_Mean = mean(VALUE_KG_CAP), .groups ='drop') %>% 
  arrange(desc(VALUE_KG_CAP_Mean))
View(meatdf_kg_type)

```
```{r, echo=FALSE}
ggplot(data = meatdf_kg_type, aes(x = SUBJECT, y = VALUE_KG_CAP_Mean, fill = SUBJECT)) + 
  geom_bar(stat = "identity", width = 0.5) +
labs(title = 'Top most consumed type of meat:1990-2026', main= 0.5 , subtitle = 'unit: kg per cap')

```




This graph was used to analyze the annual meat consumption per capita and to examine which types of meat are consumed the most. At first glance, chicken meat stands out as the type of meat whose average gram consumed per capita is the highest for almost all years. In addition, lamb and beef consumption figures show a downward trend, while pork consumption figures follow a horizontal line. According to these data, it cannot be said that there has been a big shift in meat consumption, but it can be concluded that chicken meat is a more preferable type of meat due to the increase in chicken consumption.





```{r, echo=FALSE}
meatdf_kg_time <- meatdf_kg %>% 
  group_by(TIME, SUBJECT) %>% 
  summarize(VALUE_KG_CAP_Mean = mean(VALUE_KG_CAP))
```
```{r, echo=FALSE}
ggplot(data = meatdf_kg_time, aes(x = TIME, y = VALUE_KG_CAP_Mean, group = SUBJECT)) +
  geom_line(linetype = 'dashed', size = 1.2, aes(color = SUBJECT)) +
  geom_point(size = 3, aes(color = SUBJECT)) + 
  labs(title = 'The evolution of meat consumption per cap by years', subtitle = 'unit: kg/cap')

```





This graph shows which types of meat are consumed more in per capita meat consumption over the years and how this consumption has developed.

Looking at the graph, it can be seen that the consumption of chicken meat is increasing rapidly and, unlike all other types of meat, shows a constantly rising trend. In addition, red meat, namely beef, lamb and pork, has shown a marked decreasing trend in recent years. However, due to a relatively slight increase in total meat consumption, chicken meat consumption increased, while red meat consumption decreased.

This graph helps us to easily Decipher the trends in meat consumption over the years and shows that chicken meat has an increasing popularity among all other types of meat.




```{r, echo=FALSE}
ggplot(data = meatdf_kg_type %>% group_by(SUBJECT)%>% slice(1:5), aes(fill=LOCATION, x = SUBJECT, y = VALUE_KG_CAP_Mean))+
  geom_bar(position = 'dodge', stat = 'identity') +
  labs(title = '1990-2026:Top 5 most meat consumption countries by type', subtitle = 'unit: kg/cap')

```




The purpose of this graph is to show the top 5 countries with the highest per capita consumption of various meat types.

Looking at the graph, it can be observed that chicken is the most consumed meat type, indicating an increase in chicken meat consumption in the majority of the five countries. It is also noteworthy that among these five countries, there are developed countries such as the United States, Australia, and Canada, with high levels of meat consumption.

This graph provides an insight into the meat consumption of countries worldwide based on meat types. Additionally, it demonstrates that chicken meat consumption is the highest among all meat types and that meat consumption is particularly high in some countries, especially in developed countries.

```{r echo=FALSE}
et1 <- meatdf_kg_type$VALUE_KG_CAP_Mean[meatdf_kg_type$SUBJECT == "Beef"]
et2 <- meatdf_kg_type$VALUE_KG_CAP_Mean[meatdf_kg_type$SUBJECT == "Sheep"]
et1 <- c(27.721815, 24.460362, 23.282770, 20.130336)
et2 <- c(19.26238,14.888964, 8.044462, 8.643369)

t.test(et1, et2)

```
I checked the consumption rate of beef and sheep meat with a T-test every 10 years.


# Conclusion
After analyzing, it can be concluded that there is no significant correlation between the type of meat and the consumption amount. Although chicken meat is the most popular among all types of meat, it cannot be concluded that chicken consumption will continue to rise and dominate the meat market in the future.

The first graph shows that chicken is more preferred among all types of meat compared to beef and pork. The second graph reveals that chicken is the most consumed type of meat worldwide, but we also observe a decline in red meat consumption. The third graph indicates the top five countries with the highest meat consumption rates, with chicken consumption leading the way in most countries.

Although we did not find a direct relationship between meat types and the amount being consumed, this analysis provides valuable insights into global meat consumption patterns. To improve this analysis in the future, more data could be collected to cover a longer time frame or a larger sample size of countries. It could also be beneficial to include the environmental impact of meat consumption and consumers' attitudes towards animal welfare in this analysis.

In conclusion, our analysis suggests there is no significant correlation between meat types and the amount being consumed. However, chicken meat remains the most popular among all types of meat and the decline in red meat consumption suggests that consumer preferences and habits may change over time.


\newpage
# References {#references}
<div id="refs"></div>

